Repeatability Test

### 2017-09-30 mlppi-ksii17/review/review_response.tex

\rev{
The table in Page3 does not have any caption to introduces besides, its location is badly organized.
}
Thanks for the comments. To address your concern, we put in tabular form the table with its caption on page~2 (now, {\color{blue}Tab.~2}). 
Note that we tabularized other examples for better exposition in the introduction.

\rev{
The main contribution of the paper is so limited and needs to be extended in Section 1. 
} 
We took out some contributions mentioned in Section 2 (now Section 3) and then incorporated them into the contribution paragraph (on page~5 
in the revision), which is now substantially extended.

\rev{ 
In the experiment environmental setting, the deployment in realistic datasets are missing and must be indicated for the reproduction of the future readers.  
}

%Even though our query workloads (similar to {\em q1} in Tab.~3) are synthetic, the queries were generated from a realistic query template, 
%which is from customer cases like reports and form templates. The queries are of type joining a fact table and a dimension table in a popular benchmark, representing a real analytical workload. In addition, the proposed wizard allows for general expressions for partitioning definition as addressed in the solution paragraph in the introduction. Hence, the results on our workloads do not lose their validity on a real environment. Please refer to the third and subsequent paragraphs in Section~5.1 (on page 16).
%The synthetic queries used for our experiments were generated from a realistic query template, which is from customer cases like reports and form templates. The queries are of type joining a fact table and a dimension table in a popular benchmark, representing a real analytical workload. 
%In addition, the proposed wizard allows for general expressions for partitioning definition as addressed in the solution paragraph in the introduction. Hence, the results on our workloads do not lose their validity on a real environment. For more details, please refer to the Solution paragraph in the introduction and the third and subsequent paragraphs in Section~5.1.
Please see the paragraph of `Workload Generation \& Deployment' in Section~5.1: more specifically, the third---fifth
paragraphs in that section, where we address the use of synthetic queries in general from to represent a realistic scenario and have a mention of reproducibility of our work.

@@

\clearpage
\section*{Reviewer 2}\label{sec:rev2}

% 2
\rev{
Reviewing: 2

Comments to the Author
The paper could be published after addressing following comments:
1. Abstract could be better write, in this reviewer point of view, the current abstract is not comprehensive.
}

OK, we rewrote the abstract.

\rev{
2. The manuscript could be better organize as well. For instance, the related works section could be placed after introduction section no before conclusion.
}
A great suggestion. We have relocated the related work section right after the introduction in the revised manuscript. Note also that there are some new references mentioned in the last paragraph of the related work.

### 2017-10-06 pt_characterization/rep_check/res1.tex
MLPPI paper
updates on the draft

\paragraph{Stacked Histograms in a 3D Plot:}
Figure~\ref{fig:hist3d} represents a 3D plot of collecting the histograms of PT in Section~\ref{sec:1st_pt}. 
Note that we additionally include the histograms from the task lengths of 8192 and 16384 seconds, which will be shown in Figures~\ref{fig:inc8192_r2_hist_v5} and~\ref{fig:inc16384_r2_hist_v5} (on page~47). See the legend in the right hand side of the figure, for more details about specific task length information.
%To obtain the better shape, we remove from those histograms outliers identified via the second step of EMPv5.
The x-axis corresponds to the normalized PT relative to the minimum, ranging 0 to 100, the y-axis to task length in log scale, and the z-axis to the normalized frequency relative to the highest bar for each histogram.

There are several interesting things to notice. First, INC32 has some empty bins in the raw histogram in Figure ~\ref{fig:inc32_r1_et_hist_v5}, thereby zero value on the x-axis for that histogram in brown in Figure~\ref{fig:hist3d}.

@@

\paragraph{Fitting PT Histograms in Bi-Normal Distributions:}
We ran Rob's code to obtain a bi-normal fit for each INC's PT histogram 
in Section~\ref{sec:first_run}. 
Table~\ref{tab:binormal_fit} exhibits the two means (modes), standard deviations, and scales for the PT histogram associated with each INC.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|} \hline
INC        & Mean 1 & Mean 2 & Std 1 & Std 2 & Scale 1 & Scale 2\\ \hline
INC1      & 1.66  & 4.73 & 1.03 & 0.54 & 0.104788 & 0.895212\\ \hline
INC2      & 2.33  & 7.07 & 2.38 & 0.54 & 0.159807 & 0.840193\\ \hline
INC4      & 2.17  & 7.89 & 0.99 & 0.86 & 0.209242 & 0.790758\\ \hline
INC8      & 3.51  & 9.15 & 1.10 & 1.08 & 0.388976 & 0.611024\\ \hline
INC16    & 4.04  & 9.53 & 0.98 & 1.28 & 0.828952 & 0.171048\\ \hline
INC32    & 2.76  & 8.26 & 1.28 & 1.12 & 0.725687 & 0.274313\\ \hline
INC64    & 6.36  & 12.02 & 1.64 & 1.62 &  0.347095 & 0.652905\\ \hline
INC128  & 4.21  & 8.64 & 1.82 & 3.40 & 0.410859 & 0.589141\\ \hline
INC256  & 6.08  & 14.61  & 3.59 & 3.75 & 0.124312 & 0.875688\\ \hline
INC512  & 1.60  & 12.43   & 11.51 & 4.47 & 0.075758 & 0.924242\\ \hline
INC1024 & 1.13  & 18.88  & 14.99 & 6.01 & 0.055255 & 0.944745\\ \hline
INC2048 & 29.93 & 52.92 & 8.53 & 6.59 & 1.001873 & -0.00187\\ \hline
INC4096 & 39.57 & 98.00 & 12.41 & 8.19 & 0.939756 & 0.060244\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Two means in mode computed for each INC~\label{tab:binormal_fit}}
\end{table}

>>>>

\paragraph{Stacked Histograms in a 3D Plot:}
Figure~\ref{fig:hist3d} represents a 3D plot of collecting the histograms of PT in Section~\ref{sec:1st_pt}. 
Note that we additionally include the histograms from the task lengths of 8192 and 16384 seconds, which will be shown in Figures~\ref{fig:inc8192_r2_hist_v5} and~\ref{fig:inc16384_r2_hist_v5} (on page~47). See the legend in the right hand side of the figure, for more details about specific task length information. 
(To obtain the better shape, we could remove from those histograms the outliers that are identified via the second step of EMPv5.)
The x-axis corresponds to the normalized PT relative to the minimum, ranging 0 to 100, the y-axis to task length in log scale, and the z-axis to the normalized frequency relative to the highest bar for each histogram.

One thing to notice is that there are some runs having a few empty bins 
in their respective histogram. For instance, INC32 has such an empty bin as shown in Figure~\ref{fig:inc32_r1_et_hist_v5}. 
Same with INC256 in Figure~\ref{fig:inc256_r1_et_hist_v5}. For such an INC run, the z-axis associated with its histogram has the zero value on the x-axis in Figure~\ref{fig:hist3d}.

@@

\paragraph{Fitting PT Histograms in Bi-Normal Distributions:}
We ran Rob's code to obtain a bi-normal fit for each INC's PT histogram 
in Section~\ref{sec:first_run}. 
Table~\ref{tab:binormal_fit} exhibits the total range of bins, the two means (modes), standard deviations, scales (weights) 
for the PT histogram, and figure numbers associated with each INC.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|} \hline
INC        & Total Range & Mean 1 & Mean 2 & Std 1 & Std 2 & Scale 1 & Scale 2 & Figures \\ \hline
INC1      & 6 & 1.66  & 4.73 & 1.03 & 0.54 & 0.10 & 0.90  & Fig.~\ref{fig:inc1_r1_hist_v5}\\ \hline
INC2      & 9 & 2.33  & 7.07 & 2.38 & 0.54 & 0.16 & 0.84  & Fig.~\ref{fig:inc2_r1_hist_v5} \\ \hline
INC4      & 9 & 2.17  & 7.89 & 0.99 & 0.86 & 0.21 & 0.79  & Fig.~\ref{fig:inc4_r1_hist_v5} \\ \hline
INC8      & 9 & 3.51  & 9.15 & 1.10 & 1.08 & 0.39 & 0.61  & Fig.~\ref{fig:inc8_r1_hist_v5}\\ \hline
INC16    & 10 & 4.04  & 9.53 & 0.98 & 1.28 & 0.83 & 0.17  & Fig.~\ref{fig:inc16_r1_hist_v5}\\ \hline
INC32    & 22 & 2.76  & 8.26 & 1.28 & 1.12 & 0.73 & 0.27  & Fig.~\ref{fig:inc32_r1_hist_v5}\\ \hline
INC64    & 14 & 6.36  & 12.02 & 1.64 & 1.62 &  0.35 & 0.65  & Fig.~\ref{fig:inc64_r1_hist_v5}\\ \hline
INC128  & 16 & 4.21  & 8.64 & 1.82 & 3.40 & 0.41 & 0.59  & Fig.~\ref{fig:inc128_r1_hist_v5}\\ \hline
INC256  & 38 & 6.08  & 14.61  & 3.59 & 3.75 & 0.12 & 0.88  & Fig.~\ref{fig:inc256_r1_hist_v5}\\ \hline
INC512  & 20 & 1.60  & 12.43   & 11.51 & 4.47 & 0.08 & 0.92  & Fig.~\ref{fig:inc512_r1_hist_v5}\\ \hline
INC1024 & 40 & 1.13  & 18.88  & 14.99 & 6.01 & 0.06 & 0.94 & Fig.~\ref{fig:inc1024_r1_hist_v5}\\ \hline
INC2048 & 65 & 29.93 & 52.92 & 8.53 & 6.59 & 1.00 & -0.00 & Fig.~\ref{fig:inc2048_r1_hist_v5}\\ \hline
INC4096 & 65 & 39.57 & 98.00 & 12.41 & 8.19 & 0.94 & 0.06  & Fig.~\ref{fig:inc4096_r1_hist_v5}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Two means in mode computed for each INC~\label{tab:binormal_fit}}
\end{table}
